Proposed Solution

### 2017-01-21 CAV17/secs/arch.tex
cav17: training set

\begin{figure*}[tbp] \centering
\includegraphics[width=0.88\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both sample configuration datasets and users' input
  configuration files to verify.
  The blue dashed box is \app. 
  The yellow components are key modules of \app.
  The purple circle is a checker for checking whether the target
  configuration file violates any rule.}
\label{fig-overview}
\end{figure*}

@@

\para{Initial phase.}
We start with the assumption 
that we are given a number of (not necessarily correct) 
configuration files, called {\em sample dataset}, 
belonging to the same system, such as MySQL or Apache. 
These files, therefore, follow similar patterns.
%In the following steps,
%we will exploit in a collection of learning algorithms 
%to build rules that describe a language model for the files.

\para{Translator.}
The translator module first parses the input sample 
dataset of configuration files, and then transforms them into 
a more structured and typed intermediate representation.
When we infer the types of entries in a configuration file, 
the type of an entry cannot always be fully determined from 
a single value, since it is very hard to understand
the purposes of key-value entries in modern
software configuration files~\cite{xu15hey}.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later use these more structured files
as a training set to learn the rules.

>>>>

\begin{figure*}[tbp] \centering
\includegraphics[width=0.88\textwidth]{figs/overview}
\caption{\app's workflow. The green components represent configuration 
  files, including both training set of configuration files and users' input
  configuration files to verify.
  The blue dashed box is \app. 
  The yellow components are key modules of \app.
  The purple circle is a checker for checking whether the target
  configuration file violates any rule.}
\label{fig-overview}
\end{figure*}

@@

\para{Initial phase.}
We start with the assumption 
that we are given a number of (not necessarily correct) 
configuration files, called {\em training set}, 
belonging to the same system, such as MySQL or Apache. 
These files, therefore, follow similar patterns.
%In the following steps,
%we will exploit in a collection of learning algorithms 
%to build rules that describe a language model for the files.

\para{Translator.}
The translator module first parses the input training  
set of configuration files, and then transforms them into 
a more structured and typed intermediate representation.
When we infer the types of entries in a configuration file, 
the type of an entry cannot always be fully determined from 
a single value, since it is very hard to understand
the purposes of key-value entries in modern
software configuration files~\cite{xu15hey}.
We address this problem 
by introducing {\em probabilistic types}.
Rather than giving a variable a single type, 
we assign several types over a probability distribution. 
We can later use these more structured files
as a training set to learn the rules.
